Reply To Examiners

### 2014-04-12 answer_thesis_examiner/chap1.tex
auto

>>>>

In page 14 of the returned thesis, Examiner No. 1 wonders ``Does the intagration of the PDF given for $A_x, A, I$ sum up to 1?''.
First I would like to thank Examiner No. 2 for raising such a question.
By going through his question, I realized that a negative sign were missed in the equation for $pdf(A_x)$.
With that corrected, let me repeat the Equations here

\begin{align}
pdf(A_x) = \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}} \\
pdf(A) = \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}} \\
pdf(I) = \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}}
\end{align}

For the first equation, consider the standard PDF equation for normal distribution centering around $\mu$ and having variance $\sigma$ given below

\begin{align}
pdf(x) = \frac{1}{\sigma \sqrt{2\pi}} e^{- \frac{(x-\mu)^2}{2 \sigma^2}}
\end{align}

Clearly, $A_x$ follows the normal distribution with expectation $avg(A_x)=0$ and variance $var(A_x)=\frac{\sigma}{\sqrt{2}}$.

Next consider the standard PDF equation for chi-square distribution with $k$ degree of freedom given below:

\begin{align}
pdf(x) = \frac{x^{\frac{k}{2}-1}e^{-x/2}}{\Gamma(k/2)2^{k/2}}
\end{align}

Set $k=2$, and thus $\Gamma(k/2)=\Gamma(1)=1$, then:

\begin{align}
pdf(x) = \frac{e^{-x/2}}{2} 
\end{align}

Set $\frac{x}{2} = \frac{A^2}{\sigma^2}$ or $x = \frac{2A^2}{\sigma^2}$, thus $\frac{dx}{dA} = \frac{4A}{\sigma^2}$.
Variable change theorem give us:

\begin{align}
pdf(A) = \frac{e^{-A^2/\sigma^2}}{2} \frac{4A}{\sigma^2} = \frac{2A}{\sigma^2} e^{-\frac{A^2}{\sigma^2}}
\end{align}

For the $pdf(I)$, if we set $\lambda = \frac{1}{\sigma^2}$ then the equation turns out to be the standard PDF equation for the Exponential Distribution

\begin{align}
pdf(x) = \lambda e^{- \lambda x}
\end{align}

### 2014-04-12 answer_thesis_examiner/chap3.tex
auto

Since Examiner No. 3 presneted his comments and suggestions in the order of the thesis' chapters, 
  I would follow his suite.

@@

I appreciate the fact that the examiner noted: ``The overall organization of the thesis is appropriate''.
Besides the issue of appropriate headings for chapter 3 and 4, which will be discussed in their respective section, minor editions have been included to address his other concerns.

\begin{itemize}
  \item \textbf{Page ii of Contents page is missing:} This is probably an administrative mistake and oversight from us. Please accept our appologies!
  \item \textbf{Usually, a Glossary is put at the end of the document: } Updated (now the Glossary section stays at the end of the thesis)
  \item \textbf{Some page number missing: } Updated (TODO: mostlikely this is an option that has been accidently turned on in the Latex Class file.)
  \item \textbf{List of source codes: } Updated (now called ``List of Pseudocodes'' as suggested by the Examiner.)
\end{itemize}

@@

The abstract has been updated so that: 1. each of the proposed models have their own name and 2. not only the benefits are listed, but also their shortcomings.

@@

The examiner suggests that ``Table captions appears at the top of a table, rather than below it'' and the chapter as well as the thesis has been updated accordingly.
The chapter is also updated, so that new and existing references are added to provide direct support.
The author's publication list is now also included in this, as well as in the final conclusion, chapter.

At this juncture, I would also wish to address one of Examiner No. 3's main concern.
It is termed as: ``it doesn't mean that by fitting a homoskedastic model to heteroskedastic data, these algorithm will give correct results''.
The approach described in this thesis differs slightly from ``fitting a homoskedastic model to heteroskedastic data''.
Here, I proposed to used log-transformation which has long been noted as converting the data from mutiplicative to additive domain.
The model for the data in this additive domain has been derived and accepted in (TODO:CITE Arsenault).
My work, in simple terms, suggests that in addition to additive properties, the transformed domain also exhibits homoskedastic properties as contrast to the heteroskedastic properties in the original domain.
These properties are investigated in this thesis to show that it does offers several benefits (for example: in designing and evaluating speckle filters).
It should be noted that the model for SAR used in this thesis is exactly the same as the additive model proposed by Arsenault (TODO:CITE) and is mathematically equivalent to the model multiplicative model for SAR data in its original domain.

@@

Chapter 2 is also updated to address Examiner No. 3's concerns.
In a bid of not confusing other examiners, I have decided not to move the theory section into a separate chapter.
However, this chapter is heavily updated so that 1. Section 2.1 is shortened considerably and 2. Section 2.2 is extended significantly. 
This I believe leads to a better balance between describing the nature of the data, and reviewing the related work.
This also help growing the space dedicated to the discussion of ``Other approaches that have recently been pursued in the research community (SAR speckle filters)''.

@@

>>>>

Since Examiner No. 3 presented his comments and suggestions in the order of the thesis' chapters, 
  I would follow his suite.

@@

Examiner No. 3 noted: ``The overall organization of the thesis is appropriate''.
Still minor editions have been included to address his  other concerns:

%I appreciate the fact that the examiner noted: ``The overall organization of the thesis is appropriate''.
%Besides the issue of appropriate headings for chapter 3 and 4, which will be discussed in their respective section, minor editions have been included to address his other concerns.

\begin{itemize}
  \item \textbf{Page ii of the Contents section is missing:} This were probably an administrative mistake and oversight from us. Please accept our apologies!
  \item \textbf{Usually, a Glossary is put at the end of the document: } Updated (now the Glossary section stays at the end of the thesis)
  \item \textbf{Some page number missing: } Updated. 
  \item \textbf{List of source codes: } Updated (now ``List of Pseudocodes'' as suggested.)
\end{itemize}

@@

The abstract has been updated so that:
\begin{enumerate}[topsep=0pt]
  \item Each of the proposed models have their own name and
  \item Not only the benefits of the proposed models are listed, but so are their shortcomings.
\end{enumerate}

@@

The examiner suggests that ``Table captions appears at the top of a table, rather than below it''. 
This suggestion has been updated in this chapter, as well as through out the whole thesis.
Also references are included to increase the persuasion power of the claims.
The list of publication is also now included in this chapter, in addition to the existing one found in the final chapter.

At this juncture, I would also wish to address one of Examiner No. 3's main concern.
He wonders: ``What makes you think that this model is appropriate?''.
Before the answer is laid out , I wish to make a few points.
First, I thank the Examiner to raise this question, which no doubt is an important one. 
Second, while it is important to judge the end result, 
  I am not quite sure that should be done at the very first chapter.
In fact, a large portion of the final chapter is devoted towards such a discussion.

To directly address the Examiner's concern, let me iterate a few points that has been noted in the thesis.
First the generic model proposed in this thesis is applicable to multi-dimensional POLSAR data.
Second, when the multi-dimensional data is collapsed into one dimensional, 
  the specific case of the proposed model matches perfectly with the model proposed for SAR by Arsenault \cite{Arsenault_JOptSocAm_1976}. 
Thus, I believe, the proposed generic model is at least as appropriate as the widely-accepted model cited above.

%It is termed as: ``it doesn't mean that by fitting a homoskedastic model to heteroskedastic data, these algorithm will give correct results''.
%The approach described in this thesis differs slightly from ``fitting a homoskedastic model to heteroskedastic data''.
%Here, I proposed to used log-transformation which has long been noted as converting the data from mutiplicative to additive domain.
%The model for the data in this additive domain has been derived and accepted in \cite{Arsenault_JOptSocAm_1976}.
%My work, in simple terms, suggests that in addition to additive properties, the transformed domain also exhibits homoskedastic properties as contrast to the heteroskedastic properties in the original domain.
%These properties are investigated in this thesis to show that it does offers several benefits (for example: in designing and evaluating speckle filters).
%It should be noted that the model for SAR used in this thesis is exactly the same as the additive model proposed by Arsenault \cite{Arsenault_JOptSocAm_1976} and is mathematically equivalent to the model multiplicative model for SAR data in its original domain.

@@

For Chapter 2, Examiner No. 3's suggests: ``Perhaps the theory section can be moved to a separate chapter, so that more space can be dedicated to the discussion of related work''.
In a bid of not confusing other examiners, however, I have decided not to move the theory section into a separate chapter.
Still, this chapter is heavily updated so that: 
\vspace{-3mm}
\begin{enumerate}
  \item Section 2.1 is shortened considerably and 
  \item Section 2.2 is extended significantly. 
\end{enumerate}

This I believe leads to a better balance between describing the nature of the data and reviewing the related work.
%This also help growing the space dedicated to the discussion of ``Other approaches that have recently been pursued in the research community (SAR speckle filters)''.

@@

\bibliographystyle{apalike}
\bibliography{answer_document}
